QCL: Added value of differential correlation

### 2012-01-05 inst/doc/article.Rnw
New dataset and resaved data

<<echo=FALSE,results=hide>>=
  require(qcl)
  set.seed(200)
  data(ath.metabolites) # Arabidopsis Thaliana dataset
  cat("QCL scan\n")
  qcl_result <- QCLscan(ath.metab$genotypes, ath.metab$phenotypes, 1:24, n.perm=250)
@

@@

\begin{figure}[ht]
  \centering
<<permutation_scores, fig=TRUE, echo=FALSE, height=3.0>>=
op <- par(cex=0.5)
hist(qcl_result,c(3,2,1))
op <- par(cex=1)
@ 
  \caption{QCL scores obtained during permutations (A. Thaliana) additional information obtained by QCL mapping, 
  which can be used to reconstruct the underlying genetic architecture.\label{fig:histPermAra}}
\end{figure}

\begin{figure}
  \centering
<<singletrait, fig=TRUE, echo=FALSE, height=3.0>>=
op <- par(cex=0.5)
plot(qcl_result[[1]])
op <- par(cex=1)
@
  \caption{QCL profile (A. Thaliana, X3.Hydroxypropyl) transformed to LOD scores compared to the QTL profile of the same phenotype, We see an 
  additional significant peek for this phenotype (Between Marker 50 to 60) \label{fig:singletrait}}
\end{figure}

\begin{figure}
  \centering
<<singletraitLOD, fig=TRUE, echo=FALSE, height=3.0>>=
op <- par(cex=0.5)
QCLasLOD(qcl_result[[1]], qcl_result[[1]]$qtl)
op <- par(cex=1)
@ 
  \caption{QCL profile (A. Thaliana, X3.Hydroxypropyl) transformed to LOD scores. Shown is the likelyhood contribution of each of 
  the 24 metabolites to the QCL profile. \label{fig:singletraitLOD}}
\end{figure}

\begin{figure}[ht]
  \centering
<<p2mmatrix, fig=TRUE, echo=FALSE, height=3.0>>=
par(mar=c(3,8,1.1,1.1))
plot(qcl_result, against="markers", do.grid=TRUE, grid.col="white")
@ 
  \caption{Phenotypes x Markers matrix (A. Thaliana) this is 'comparable' to a QTL scan on multiple traits.\label{fig:p2mmatrix}}
\end{figure}

\begin{figure}[ht]
  \centering
<<QTLmatrix, fig=TRUE, echo=FALSE, height=3.0>>=
par(mar=c(3,8,1.1,1.1))
QTLimage(qcl_result, do.grid=TRUE, grid.col="white")
@
  \caption{Heatmap showing QTL scores for all 24 metabolities in A. Thaliana.\label{fig:QTLmatrix}}
\end{figure}

\begin{figure}[ht]
  \centering
<<p2pmatrix, fig=TRUE, echo=FALSE, height=3.0>>=
par(mar=c(3,8,1.1,1.1))
plot(qcl_result, against="phenotypes", do.grid=TRUE, grid.col="white")
@ 
  \caption{Phenotypes x Phenotypes matrix (A. Thaliana) additional information obtained by QCL mapping, 
  which can be used to reconstruct the underlying genetic architecture.\label{fig:p2pmatrix}}
\end{figure}

>>>>

<<echo=FALSE,results=hide>>=
  require(qcl)
  set.seed(200)
  data(ath.result)
@

@@

\begin{figure}[ht]
  \centering
<<permutation_scores, fig=TRUE, echo=FALSE, height=3.0>>=
op <- par(cex=0.5)
hist(ath.result,c(3,2,1))
op <- par(cex=1)
@ 
  \caption{QCL scores obtained during permutations (A. Thaliana) additional information obtained by QCL mapping, 
  which can be used to reconstruct the underlying genetic architecture.\label{fig:histPermAra}}
\end{figure}

\begin{figure}
  \centering
<<singletrait, fig=TRUE, echo=FALSE, height=3.0>>=
op <- par(cex=0.5)
plot(ath.result[[1]])
op <- par(cex=1)
@
  \caption{QCL profile (A. Thaliana, X3.Hydroxypropyl) transformed to LOD scores compared to the QTL profile of the same phenotype, We see an 
  additional significant peek for this phenotype (Between Marker 50 to 60) \label{fig:singletrait}}
\end{figure}

\begin{figure}
  \centering
<<singletraitLOD, fig=TRUE, echo=FALSE, height=6.0>>=
op <- par(cex=0.5)
QCLasLOD(ath.result[[1]], ath.result[[1]]$qtl)
op <- par(cex=1)
@ 
  \caption{QCL profile (A. Thaliana, X3.Hydroxypropyl) transformed to LOD scores. Shown is the likelyhood contribution of each of 
  the 24 metabolites to the QCL profile. \label{fig:singletraitLOD}}
\end{figure}

\begin{figure}[ht]
  \centering
<<p2mmatrix, fig=TRUE, echo=FALSE, height=3.0>>=
par(mar=c(3,8,1.1,1.1))
plot(ath.result, against="markers", do.grid=TRUE, grid.col="white")
@ 
  \caption{Phenotypes x Markers matrix (A. Thaliana) this is 'comparable' to a QTL scan on multiple traits.\label{fig:p2mmatrix}}
\end{figure}

\begin{figure}[ht]
  \centering
<<QTLmatrix, fig=TRUE, echo=FALSE, height=3.0>>=
par(mar=c(3,8,1.1,1.1))
QTLimage(ath.result, do.grid=TRUE, grid.col="white")
@
  \caption{Heatmap showing QTL scores for all 24 metabolities in A. Thaliana.\label{fig:QTLmatrix}}
\end{figure}

\begin{figure}[ht]
  \centering
<<p2pmatrix, fig=TRUE, echo=FALSE, height=3.0>>=
par(mar=c(3,8,1.1,1.1))
plot(ath.result, against="phenotypes", do.grid=TRUE, grid.col="white")
@ 
  \caption{Phenotypes x Phenotypes matrix (A. Thaliana) additional information obtained by QCL mapping, 
  which can be used to reconstruct the underlying genetic architecture.\label{fig:p2pmatrix}}
\end{figure}
